aircraft-pfp

### 2024-08-26 examples/aircraft-pfp.Rmd
vert plot aircraft flask

```{r obs_plot_vertt, fig.width=7, fig.height=5, eval = F}
x <- df3
x$ch4 <- x$value*1e+9
obs_plot(x[site_code == "IAGOS"], 
         time = "ch4", 
         y = "altitude_final", 
         colu = "month", #n = c(1L, 3L, 6L, 8L, 9L, 11L, 12L), 
         type = "b", 
         xlab = expression(CH[4]~ppb), 
         ylab = "altitude (m)")
```

>>>>

```{r obs_plot_vertt, fig.width=7, fig.height=5, eval = F}
x <- df3
x$ch4 <- x$value*1e+9
obs_plot(x, 
         time = "ch4", 
         y = "altitude_final", 
         colu = "site_code", #n = c(1L, 3L, 6L, 8L, 9L, 11L, 12L), 
         type = "b", 
         xlab = expression(CH[4]~ppb), 
         ylab = "altitude (m)")
```
